Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-15 doc/manuscript/ESSDmanuscript.Rmd
start on section 3

# Mapping ForC to EFDB
ForC data is incredibly valuable to EFDB and there is data which is included in the ForC database that does not meet EFDB standards. There were two main EFDB guidelines which limits the amount of data we could transfer. EFDB will not accept data which has been digitized(from graph) and ForC does.

@@

EFDB data submissions require information that was not recorded in previous versions of ForC.
It was therefore necessary to return to original publications to retrieve relevant information, including ...

>>>>

# Mapping ForC to EFDB

The majority of information required by EFDB was present in previous versions of ForC [].
We made modest structural changes to ForC (Table ##) to allow complete records to be restructured for automated population of EFDB data entry forms using R ().

@@

EFDB data submissions require information that was not recorded in previous versions of ForC.
It was therefore necessary to return to original publications to retrieve relevant information, including the following:

- Data location within source - Because EFDB will not accept data which has been digitized (from graphs) while ForC does, it was necessary to review and note the location of the data within the original source

### 2022-04-15 doc/manuscript/ESSDmanuscript.tex
start on section 3

ForC data is incredibly valuable to EFDB and there is data which is
included in the ForC database that does not meet EFDB standards. There
were two main EFDB guidelines which limits the amount of data we could
transfer. EFDB will not accept data which has been digitized(from graph)
and ForC does.

@@

EFDB data submissions require information that was not recorded in
previous versions of ForC. It was therefore necessary to return to
original publications to retrieve relevant information, including
\ldots{}

>>>>

The majority of information required by EFDB was present in previous
versions of ForC {[}{]}. We made modest structural changes to ForC
(Table \#\#) to allow complete records to be restructured for automated
population of EFDB data entry forms using R ().

@@

EFDB data submissions require information that was not recorded in
previous versions of ForC. It was therefore necessary to return to
original publications to retrieve relevant information, including the
following:

\begin{itemize}
\tightlist
\item
  Data location within source - Because EFDB will not accept data which
  has been digitized (from graphs) while ForC does, it was necessary to
  review and note the location of the data within the original source
\end{itemize}
